### 2013-06-07 report/report-1.Rmd
Refine Emial and report

@@

**Reference:** `r formatBib(paste0("../", as.character(.dat$ref$reference)))[[1]]`

@@

@@

**Stand description**

@@

This is how the study `r .study` (each color represents a species) fits in the entire dataset (grey).

>>>>

```{r, echo=FALSE}

locLevelInfo  <-  function(data){

  vars <- c("location","longitude","latitude","vegetation")

  loc <- data[!duplicated(data[,vars]),vars]

  loc[is.na(loc) | loc=="" | loc=="NA"]  <-  "missing"  
  return(loc)
}

standLevelInfo  <-  function(data){

  vars <- c("location","grouping","growingCondition","status")
  sta <- data[!duplicated(data[,vars]),vars]

  if(all(is.na(sta$grouping)))
    sta  <-  sta[,-which(names(sta) == "grouping")]

  sta[is.na(sta) | sta=="" | sta=="NA"]  <-  "missing"

  return(sta)
}

spLevelInfo  <-  function(data){
  spec         <-  data.frame(species=as.character(unique(data$species)), stringsAsFactors=FALSE)
  for(z in c("family", "pft")){
    spec[[z]]  <-  as.character(data[[z]][match(spec$species,data$species)])
    i          <-  spec[[z]]=="" | is.na(spec[[z]]) 
    if(any(i)){
      spec[[z]][i]  <-  "missing"
    }
  }
  j            <-  spec$species=="" | is.na(spec$species) 
  if(any(j)){
    spec$species[j]  <-  "missing"
  }
  spec
}

printMeta  <-  function(data){
  dataset   <-  as.character(unique(data$dataset))
  openMeta  <-  read.csv(paste0("../",dir.rawData,"/",dataset,"/studyMetadata.csv"), h=TRUE, stringsAsFactors=FALSE)
  openMeta
}

@@

## Contact Information

@@

## Citation
Information about the primary reference for the data you provided. 
```{r echo=FALSE, comment=''}
  bibfile<- paste0("../", as.character(.dat$ref$filename))
```
**Reference:** `r formatBib(bibfile)[[1]]`

**DOI:** `r  bibGetElement(bibfile, element = "doi")`

**Abstract:** `r  bibGetElement(bibfile, element = "abstract")`

@@

**Stand description**
Information about the growing condition of plants in your study, i.e. their local environment.

@@

This is how the study `r .study` (each colour represents a species) fits in the entire dataset (grey).
